Fast Sorting on Modern Computers

### 2005-06-07 paper/docs/merge.tex
removed old tarred gzips reran mergesort simulations removed .eps files from the repository made some fixes to the scripts deleted some directories which werent used, or which were old
renamed the logs directory, updated merge a tad

\plot{merge}{}{}{Results shown are for a Direct Mapped cache.}{Results shown are
for a Direct Mapped cache.}{}{}

@@

>>>>

\plot{merge}{}{}{Results shown are for a Direct Mapped cache.}{Except where
marked, results shown are for a Direct Mapped cache.}{}{}

@@

%TODO
TODO what about level 1 cache misses if we realigned by 1024?
